Adaptation of Palmer amaranth to the upper Midwest

### 2021-07-09 Frontiers/Frontiers.Rmd
LP

```{r fig1, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../june.png")
```

@@

```{r, Figure-2, ref.label = "fig1", echo = FALSE, message = FALSE, fig.height=3, fig.width=5, fig.align='center', fig.cap='Figure caption', out.width = "150mm", out.height = "85mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

>>>>

```{r fig1, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../weather/Figure 1.png")
```

```{r fig2, echo = FALSE, message=FALSE, fig.show = "hide"}
knitr::include_graphics("../june.png")
```

@@

```{r, Figure-1, ref.label = "fig1", echo = FALSE, message = FALSE, fig.height=3, fig.width=6, fig.align='center', fig.cap='Mean average temperature (C) and montly sum precipitation (mm) at Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL', out.width = "160mm", out.height = "100mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

```{r, Figure-2, ref.label = "fig2", echo = FALSE, message = FALSE, fig.height=3, fig.width=6, fig.align='center', fig.cap='Figure caption', out.width = "160mm", out.height = "90mm"}
# You can also refer to code chunks from above to place figures at the bottom.
```

### 2021-07-09 Frontiers/Frontiers.tex
LP

The doy for 10, 50, and 90\% Palmer amaranth cumulative flowering were
determined using the \emph{ED} function of drc package. Also, the 10,
50, and 90\% Palmer amaranth cumulative flowering were compared among
crop/fallow and timings using the \emph{EDcomp} function of drc package.
The EDcomp function compares the ratio of flowering timing using
t-statistics, where P-value \textless{} 0.05 indicates that we fail to
reject the null hypothesis.

@@

{\centering \includegraphics[width=150mm,height=85mm]{../june}

>>>>

The doy for 10, 50, and 90\% Palmer amaranth cumulative flowering were
determined using the \emph{ED} function of drc package. Also, the 10,
50, and 90\% Palmer amaranth cumulative flowering were compared among
crop/fallow and timings using the \emph{EDcomp} function of drc package.
The EDcomp function compares the ratio of cumulative flowering using
t-statistics, where P-value \textless{} 0.05 indicates that we fail to
reject the null hypothesis.

@@

{\centering \includegraphics[width=160mm,height=100mm]{../weather/Figure 1}

\caption{Mean average temperature (C) and montly sum precipitation (mm) at Arlington, WI, Clay Center, NE, Grant, NE, Lincoln, NE and Macomb, IL}\label{fig:Figure-1}
\end{figure}

{\centering \includegraphics[width=160mm,height=90mm]{../june}
